### 2017-07-25 introduction.tex
minor to intro

While science has long been collaborative and data driven, today, more than ever before,
researchers are dependent on technologies that enable their ability to safely store,
effectively manage, and quickly analyze vast amounts of
data. Moreover, individual datasets that are of interest to science and scholarship
vary widely in size, often take on heterogeneous structures, and command varying
levels of sensitivity. In fact, data sensitivity is often `custom' -defined specifically by
data use agreements that can be so granular as to vary from user to user and institution
to institution. At the very same time, however, a typical research setting involves
collaborators from multiple institutions that often share data, analysis techniques,
and results. This is, in fact, a cornerstone of modern research. Yet, when data are
particularly sensitive and their use agreements limit access and activities at the
level of individual users, research collaboration can either lead to inadvertent
breaches of agreement or can grind to a halt under administrative friction.

@@

Data sensitivity and security concerns are well founded. While many datasets are public, the most
valuable ones are often considered private due to legal or contractual obligations under which the data
is shared, or even governmental regulations. The limited and proprietary nature
of particular datasets can further increase perceived value to researchers given that the space of possible
questions and possible answers that can be derived from the data is, in a sense, hidden from competition.
At the same time, sensitivity adds the burden of ensuring the security of the data to the researchers.

% Ability to compute effectively and securely.
\yadu{a myriad of?}

@@

To address these challenges we introduce two abstractions:
the `safe collection' to define the scope of a data collection
and the associated policies and the role of a data `steward'
to manage safe collections. These two constructs allow us
to define, manage, and audit access, use, and export of
sensitive data.  We implement these constructs in \NAME and
describe how such implementation enhances security without compromising collaborative agility.

>>>>

While science has long been collaborative and data driven, today, more than ever before,
researchers are dependent on technologies that enable their ability to safely store,
effectively manage, and quickly analyze vast amounts of
data. Moreover, individual datasets that are of interest to science and scholarship
vary widely in size, often take on heterogeneous structures, and command varying
levels of sensitivity. In fact, data sensitivity is often `custom' -defined specifically by
data use agreements that can be so granular as to vary from user to user and institution
to institution. At the very same time, however, a typical research setting involves
collaborators from multiple institutions that often share data, analysis techniques,
and results. This is, in fact, a cornerstone of modern research. Yet, when data are
particularly sensitive and their usage agreements limit access and research activities at the
level of individual users, research collaboration can either lead to inadvertent
breaches of agreement or can grind to a halt under administrative friction.

@@

At the same time, data sensitivity and security concerns are well founded. While many datasets are public, the most
valuable ones are often considered `private' or `protected' due to legal or contractual obligations under which the data
is shared, or even, the most extreme cases, under governmental regulation. However, the limited and proprietary nature
of particular datasets can further increase perceived value to researchers given that the space of possible
questions and possible answers that can be derived from the data is, in a sense, hidden from competition.
Simultaneously, increasing sensitivity adds to the burden of ensuring the security of the data.

% Ability to compute effectively and securely.

@@

To address these challenges we introduce two abstractions:
the `safe collection' to define the scope of a data collection
and the associated policies, and the role of a data `steward'
to manage safe collections. These two constructs allow us
to define, manage, and audit access, use, and export of
sensitive data. In this paper, we describe the implementation of these constructs in \NAME and
outline how such implementation enhances security without compromising collaborative agility.
